|

### 2025-03-23 reproducibility/manuscript/manuscript.qmd
fix(manuscript): set explicit figure width percentages
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

::: {#fig-model}
![](figures/v2/Figure1.pdf)

@@

::: {#fig-model-results}
![](figures/v2/Figure2.png)

@@

::: {#fig-lineage-tracing}
![](figures/v2/Figure3.png)

@@

::: {#extfig-graphical-models}
![](figures/v2/Supplementary-Figure1.pdf)

@@

::: {#extfig-model-results}
![](figures/v2/Supplementary-Figure2.png)

@@

::: {#extfig-model-2-result}
![](figures/v2/Supplementary-Figure3.png)

@@

::: {#extfig-lineage-tracing}
![](figures/v2/Supplementary-Figure4.png)

@@

::: {#extfig-lineage-tracing-2}
![](figures/v2/Supplementary-Figure5.png)

>>>>

::: {#fig-model}
![](figures/v2/Figure1.pdf){width=98%}

@@

::: {#fig-model-results}
![](figures/v2/Figure2.png){width=98%}

@@

::: {#fig-lineage-tracing}
![](figures/v2/Figure3.png){width=98%}

@@

::: {#extfig-graphical-models}
![](figures/v2/Supplementary-Figure1.pdf){width=98%}

@@

::: {#extfig-model-results}
![](figures/v2/Supplementary-Figure2.png){width=98%}

@@

::: {#extfig-model-2-result}
![](figures/v2/Supplementary-Figure3.png){width=98%}

@@

::: {#extfig-lineage-tracing}
![](figures/v2/Supplementary-Figure4.png){width=98%}

@@

::: {#extfig-lineage-tracing-2}
![](figures/v2/Supplementary-Figure5.png){width=98%}
